Semi-Inclusive Deep Inelastic Scattering in Wandzura-Wilczek-type approximation

### 2018-05-23 tex/test-WW-type-00v-PS.tex
alexei
Saman tests
"Hello world" at abstract

\author[a]{S.~Bastami}
\author[b]{H.~Avakian}
\author[c]{A.~V.~Efremov} 
\author[d,e]{A.~Kotzinian} 
\author[f]{B.~U.~Musch} 
\author[e]{B.~Parsamyan} 
\author[g,b]{A.~Prokudin} 
\author[h]{M.~Schlegel} 
\author[i]{G.~Schnell} 
\author[a,j]{P.~Schweitzer} 
\author[a]{K.~Tezgin}
\author[j]{W.~Vogelsang}

@@

% e-mail addresses: one for each author, in the same order as the authors
\emailAdd{saman.bastami@uconn.edu}
\emailAdd{avakian@jlab.org}
\emailAdd{efremov@theor.jinr.ru}
\emailAdd{aram.kotzinian@cern.ch}
\emailAdd{bmusch@b-mu.de}
\emailAdd{bakur@cern.ch}
\emailAdd{prokudin@jlab.org}
\emailAdd{schlegel@nmsu.edu}
\emailAdd{gunar.schnell@desy.de}
\emailAdd{peter.schweitzer@phys.uconn.edu}
\emailAdd{kemal.tezgin@uconn.edu}
\emailAdd{werner.vogelsang@uni-tuebingen.de}

%\date{\today}
%===================  PREPRINT NUMBER, JOURNAL =======================
%\
%===================  ABSTRACT =======================================
%\begin{abstract}
\abstract{ 
We present the complete cross-section for pion production in semi-inclusive 
deep-inelastic scattering up to power-suppressed ${\cal O}(1/Q^2)$ terms in 
the Wandzura--Wilczek-type approximation \ps{which consists in a systematic
neglect of $\bar{q}gq$--terms with respect to $\bar{q}q$--correlators.}
We compute all twist-2 and twist-3 structure functions and the corresponding 
asymmetries, and discuss the applicability of the Wandzura--Wilczek-type 
approximations on the basis of available data. We make predictions which 
can be tested by data from Jefferson Lab, COMPASS, HERMES, and the future 
Electron-Ion Collider. The results of this paper can be readily used for 
phenomenology and for event generators, and will help to improve our 
understanding of the TMD theory beyond leading twist.
} 
%\end{abstract}
%\pacs{13.88.+e, % Polarization in interactions and scattering
%      13.85.Ni, % Inclusive production with identified hadrons
%      13.60.-r, % Photon and charged-lepton interactions with hadrons
 %     13.85.Qk} % Hadron-induced inclusive production with identified leptons, 
                % photons, or other nonhadronic particles (energy > 10 GeV)
\keywords{
	Wandzura--Wilczek approximation, 
	semi-inclusive deep inelastic scattering, 
	transverse momentum dependent distribution functions, 
	spin and azimuthal asymmetries, leading and subleading twist}

@@

The presently available phenomenological information on $g_T^a(x)$ is due 
to measurements of the structure function $g_2(x)$, Eq.~(\ref{Eq:DIS-g2}),
in DIS off various transversely polarized targets. In the WW-approximation 
(\ref{Eq:WW-original1}) one can write $g_2(x)$ as a total derivative
expressed in terms of the experimentally well known twist-2
structure function $g_1(x)$ as follows
\be
    	g_2(x) \stackrel{\rm WW}{\approx} g_2(x)_{\rm WW} \equiv
	\frac{ d\;}{ d x}\;\Biggl[\frac{x}{2}\int_x^1\frac{ d y}{y}
	\;g_1(y)\Biggr]\,.\label{Eq:g2-in-WW-approximation}
\ee
Data support (\ref{Eq:g2-in-WW-approximation}) to a good accuracy
\cite{Anthony:2002hy,Abe:1998wq,Airapetian:2011wu}, although especially 
at smaller $x$ more stringent tests are not yet possible. Overall it has 
been estimated that the WW approximation for $g_2(x)$ and $g_T^a(x)$ works 
with an accuracy of about $40\,\%$ or better \cite{Accardi:2009au}.

>>>>

\author[a]{S.~Bastami}
\author[b]{H.~Avakian}
\author[c]{A.~V.~Efremov}
\author[d,e]{A.~Kotzinian}
\author[f]{B.~U.~Musch}
\author[e]{B.~Parsamyan}
\author[g,b]{A.~Prokudin}
\author[h]{M.~Schlegel}
\author[i]{G.~Schnell}
\author[a,j]{P.~Schweitzer}
\author[a]{K.~Tezgin}

@@

% e-mail addresses: one for each author, in the same order as the authors
\emailAdd{saman.bastami@uconn.edu}
\emailAdd{avakian@jlab.org}
\emailAdd{efremov@theor.jinr.ru}
\emailAdd{aram.kotzinian@cern.ch}
\emailAdd{bmusch@b-mu.de}
\emailAdd{bakur@cern.ch}
\emailAdd{prokudin@jlab.org}
\emailAdd{schlegel@nmsu.edu}
\emailAdd{gunar.schnell@desy.de}
\emailAdd{peter.schweitzer@phys.uconn.edu}
\emailAdd{kemal.tezgin@uconn.edu}

%\date{\today}
%===================  PREPRINT NUMBER, JOURNAL =======================
%\
%===================  ABSTRACT =======================================
%\begin{abstract}
\abstract{
\SB{HELLO WORLD}
We present the complete cross-section for pion production in semi-inclusive
deep-inelastic scattering up to power-suppressed ${\cal O}(1/Q^2)$ terms in
the Wandzura--Wilczek-type approximation \ps{which consists in a systematic
neglect of $\bar{q}gq$--terms with respect to $\bar{q}q$--correlators.}
We compute all twist-2 and twist-3 structure functions and the corresponding
asymmetries, and discuss the applicability of the Wandzura--Wilczek-type
approximations on the basis of available data. We make predictions which
can be tested by data from Jefferson Lab, COMPASS, HERMES, and the future
Electron-Ion Collider. The results of this paper can be readily used for
phenomenology and for event generators, and will help to improve our
understanding of the TMD theory beyond leading twist.
}
%\end{abstract}
%\pacs{13.88.+e, % Polarization in interactions and scattering
%      13.85.Ni, % Inclusive production with identified hadrons
%      13.60.-r, % Photon and charged-lepton interactions with hadrons
 %     13.85.Qk} % Hadron-induced inclusive production with identified leptons,
                % photons, or other nonhadronic particles (energy > 10 GeV)
\keywords{
	Wandzura--Wilczek approximation,
	semi-inclusive deep inelastic scattering,
	transverse momentum dependent distribution functions,
	spin and azimuthal asymmetries, leading and subleading twist}

@@

The presently available phenomenological information on $g_T^a(x)$ is due
to measurements of the structure function $g_2(x)$, Eq.~(\ref{Eq:DIS-g2}),
in DIS off various transversely polarized targets. In the WW-approximation
(\ref{Eq:WW-original1}) one can write $g_2(x)$ as a total derivative
expressed in terms of the experimentally well known twist-2
structure function $g_1(x)$ as follows
\be
    	g_2(x) \stackrel{\rm WW}{\approx} g_2(x)_{\rm WW} \equiv
	\frac{ d\;}{ d x}\;\Biggl[x\int_x^1\frac{ d y}{y}
	\;g_1(y)\Biggr]\,.\label{Eq:g2-in-WW-approximation}
\ee
Data support (\ref{Eq:g2-in-WW-approximation}) to a good accuracy
\cite{Anthony:2002hy,Abe:1998wq,Airapetian:2011wu}, although especially
at smaller $x$ more stringent tests are not yet possible. Overall it has
been estimated that the WW approximation for $g_2(x)$ and $g_T^a(x)$ works
with an accuracy of about $40\,\%$ or better \cite{Accardi:2009au}.
